Genetic Algorithm Based Formula Generation for Curve Fitting in Time Series Forecasting Implemented as Mobile Distributed Computing

### 2019-05-12 Genetic-Algorithm-Based-Formula-Generation-for-Curve-Fitting-in-Time-Series-Forecasting-Implemented-as-Mobile-Distributed-Computing/paper.tex
Some more text was added.

Genetic algorithms are metaheuristic for global optimization inspired by the natural processes in the biological evolution. Genetic algorithms are population based and they are subset of a larger class algorithms called evolutionary algorithms. Searching for a solution with genetic algorithms is based on three general operations - selection, crossover and mutation applied over population with individuals. Each individual is a vector into the solutions space.

@@

@@

@@

@@

>>>>

Genetic algorithms are metaheuristic for global optimization inspired by the natural processes in the biological evolution. Genetic algorithms are population based \cite{mirjalili01} and they are subset of a larger class algorithms called evolutionary algorithms \cite{liu01}. Searching for a solution with genetic algorithms is based on three general operations - selection, crossover and mutation applied over population with individuals. Each individual is a vector into the solutions space.

@@

The organization of genetic algorithms computation by presence of population and operators applied over this population makes genetic algorithms perfect for parallel computations \cite{cheng01}. In distributed computing system genetic algorithm global population is used (client-server architecture) and many local sub-populations are evolved without real need for information exchange between territorial separated computers.

@@

Experiments are done as Android mobile application. On the client side Apache Commons Genetic Algorithms Framework \cite{apache01} is used. Mathematical expressions are presented and evaluated with Java build of mXparser \cite{gromada01} software library. On the server side PHP/MySQL based solution \cite{balabanov03} is responsible for synchronization and financial time series data supply.

@@

\bibitem{mirjalili01} Mirjalili S., \textbf{\textit{Genetic Algorithm}}, Evolutionary Algorithms and Neural Networks. Studies in Computational Intelligence, Springer, Cham, \textbf{780}, p. 43--55, 2019.

\bibitem{liu01} Liu, J., Abbass, H.A., Tan, K.C., \textbf{\textit{Evolutionary Computation}}, Evolutionary Computation and Complex Networks, Springer, Cham, p. 3--22, 2019.

\bibitem{cheng01} Cheng, JR., Gen, M., \textbf{\textit{Accelerating genetic algorithms with GPU computing: A selective overview}}, Computers \& Industrial Engineering, Elsevier, \textbf{128}, p. 514--525, 2019.

@@

\bibitem{apache01} \textbf{\textit{Apache Commons Genetic Algorithms Framework}}, http://commons.apache.org/proper/commons-math/userguide/genetics.html Last visited: 12-May-2019 12:36:56 EET, 2016.

\bibitem{gromada01} Gromada, M., \textbf{\textit{mXparser - Math Expression Evaluator / Parser - Library}}, http://www.mathparser.org/ Last visited: 12-May-2019 12:44:12 EET.

\bibitem{balabanov03} Balabanov, T., \textbf{\textit{Distributed System for Time Series Prediction with Evolutionary Algorithms and Artificial Neural Networks}}, Abstracts of Dissertations - Institute of Information and Communication Technologies - Bulgarian Academy of Sciences, \textbf{6}, 2017.
